\subsection{Recruiting and Rewarding Subjects}
%Unlike previous similar studies, which recruited subjects from student populations or professional red teams, in this project we want to cast a wider net. The reason is that students, by and large, are not representative of real reverse engineers, and those working on professional red teams are not willing to publicize their techniques and tools-of-the-trade.

To participate, subjects download a virtual machine image,\footnote{Kali~\cite{muniz2013web} is the preferred Linux distribution, since it already contains many reverse engineering tools, and Ubuntu is also officially supported.  Fedora support is forthcoming.} install our monitoring system from \revengeurl, and select and download one of our challenges. As part of the installation process users are also asked to give consent as required by the approval\footnote{University of Arizona IRB 1610963521.} granted by our institution's Institutional Review Board (IRB).

%After solving a challenge, users upload the solution to the \revenge site for analysis, along with the data from the monitoring system, and answers to a questionnaire which asks about their demographic background and how they experienced solving the challenge.

%Unlike previous studies who have used students as subjects (who might get course credit for solving a challenge), we need to provide more substantial incentives to encourage people to participate.
At the present time, we have allocated USD 15,000 to be given out (in amounts of USD 100, 500, or 1,000) to users who submit successful solutions. The amounts are dependent on the perceived difficulty of each challenge.

\revenge relies on the participation of reverse engineers.  The potential lack of participation in itself would present an interesting result, providing some indication of the costs of reverse engineering; increasing the rewards may be possible should this occur.  Additionally, experts and students may be compensated directly for participation in order to provide some baseline data.  We hope, however, that the goals of \revenge will also provide significant motivation to actors who have an interest in the results of the project.
